The Cluster Difference Imaging Photometric Survey (CDIPS). I. Method, Light Curves, and Planet Candidates from Sectors 6--8

### 2019-05-30 paper/ms.tex

For the astrometric solution, we use the WCS and SIP coefficients
derived by SPOC and included in the FFI headers \citep[][Sec.~8]{pence_fits_2010}.  We
explored the possibility of using \texttt{astrometry.net}
\citep{lang_2010} to derive our own astrometric solutions for each
frame, but found that the astrometric residual (the mean separation
between projected and measured positions) was consistently a factor of
1.5-2x higher in our WCS solutions than in those given by SPOC.

With the resulting WCS information, we then project a source catalog
onto each frame.  Initially, we planned to photometer all Gaia-DR2
sources in each field down to a cutoff of $G_{Rp} < 16$.  However, we
found that for the galactic plane fields this produces an excessively
large number of sources.  Our source catalog for each frame is
therefore a combination of the CDIPS target stars ($G_{Rp} < 16$), and
all Gaia-DR2 sources down to $G_{Rp} < 13$.  We use the expected
positions of these sources to center the apertures in our photometry,
rather than attempting to detect the positions.  Such
``forced-aperture photometry'' is preferable to performing source
extraction in the crowded fields that are the focus of this work.  The
Gaia-DR2 epoch is J2015.5, so even the fastest-moving stars with
proper motions of $\sim$$1\,{\rm arcsecond}\,{\rm yr}^{-1}$ are still
well within one pixel of their predicted positions in the TESS images.
The projection from catalog sky-coordinate positions to pixel
coordinates is performed using standard WCS transformations, and the
source catalog look-up is performed using
\texttt{gaia2read}\footnote{\url{github.com/samuelyeewl/gaia2read}}
\citep{kim_2018_gaia2read}.
The astrometric residual is displayed in various forms in
Figure~\ref{fig:astrometricresidual}.

Finally, we use \texttt{fiphot} to perform aperture photometry on the
bright stars from the
source list, by summing the counts inside appropriately-weighted
circular apertures centered on the projected positions from Gaia DR2. 
The pixel weights $w_{x,y}$ are equal to the fraction of the pixel
that falls within the aperture.  They are thus unity for pixels
entirely within the aperture, and fractional along the aperture
boundary (see \citealt{Pal_2009} Fig 17). 
The background levels are measured in annuli around each aperture
center.  The raw flux of the object after background removal is then
(\citealt{Pal_2009} Eq 65)
\begin{equation}
  f = \sum_{x,y} w_{x,y} (I_{x,y} - B) = f_{\rm total} - B r_0^2.
  \label{eq:simple_aperture_phot}
\end{equation}
The resulting measurements, for instance of the background level of
each aperture, and the number of ``good'' objects that are detected,
are later used as input for selecting photometric reference frames.

@@

The core operation of ``classical'' image subtraction
attempts to match a photometric reference $R$ and a target image $I$ by 
computing a convolution kernel.
The kernel, once applied to the high signal-to noise reference,
produces a model image, $M_{xy}$,
\begin{equation}
    M_{xy} = (R \otimes K)_{xy} + B_{xy},
\end{equation}
where $B_{xy}$ is a component of the model image that allows for
background variations.
We model the background separately, so we set $B_{xy}=0$.
The convolution kernel $K$ is typically decomposed onto a
basis, $K = \sum_i c_i K_i$, and the coefficients are found
by minimizing
\begin{equation}
    \chi^2 = \sum_{xy} \left( \frac{I_{xy} - M_{xy}}{\sigma_{xy}} \right)^2,
    \label{eq:chisq_conv}
\end{equation}
where $\sigma_{xy}$ is the uncertainty in the target image pixel values.
Photometry is then performed on the difference image $D_{xy}$, where
$D_{xy} = I_{xy} - M_{xy}$.
For this work, the uncertainty in each target image pixel is
taken to be a constant.

>>>>

For the astrometric solution, we use the WCS and SIP coefficients
derived by SPOC and included in the FFI headers
\citep[][Sec.~8]{pence_fits_2010}.  We explored the possibility of
using \texttt{astrometry.net} \citep{lang_2010} to derive our own
astrometric solutions for each frame, but found that the astrometric
residual (the mean separation between projected and measured
positions) was consistently a factor of 1.5-2 times higher in our WCS
solutions than in those given by SPOC (perhaps attributable to the
algorithm used to select stars and measure their positions).

With the resulting WCS information, we then project a source catalog
onto each frame.  Initially, we planned to photometer all Gaia-DR2
sources in each field down to a cutoff of $G_{Rp} < 16$.  However, we
found that for the galactic plane fields this produces an excessively
large number of sources (millions of stars per
$12^\circ\times12^\circ$ CCD).  We therefore limited our source
catalog for each frame to be
a combination of the CDIPS target stars ($G_{Rp} < 16$), and
all Gaia-DR2 sources down to $G_{Rp} < 13$.  We use the expected
projected of these sources to center the apertures in our photometry,
rather than attempting to detect the positions.  Such
``forced-aperture photometry'' is preferable to performing source
extraction in the crowded fields that are central in this work.  The
Gaia-DR2 epoch is J2015.5, so even the fastest-moving stars with
proper motions of $\sim$$1\,{\rm arcsecond}\,{\rm yr}^{-1}$ are still
well within one pixel of their predicted positions in the TESS images.
The projection from catalog sky-coordinate positions to pixel
coordinates is performed using an analog of the \texttt{wcs-rd2xy}
program that performs the standard matrix algebra \citep{lang_2010}.
The source catalog look-up is performed using
\texttt{gaia2read}\footnote{\url{github.com/samuelyeewl/gaia2read}}
\citep{kim_2018_gaia2read}.

The astrometric residual is displayed for one photometric reference
frame (to be described shortly) in
Figure~\ref{fig:astrometricresidual}.
A few salient points can be made.
First, the typical median precision of the WCS solution is a bit below
0.1 pixels, and its $90^{\rm th}$ percentile is typically less than
0.3 pixels\footnote{In fact, in our reduction we automatically impose
that the median residual and 90th percentile remain below 0.2 and 0.4
pixels, respectively.}.
The distribution has a outlier tail of saturated stars which were
masked, and thus do not have measureable centroid positions.
The errors are typically largest in the corners of the field of view,
where the non-linearity of the focal plane is most significant, and
where the corrections required by the SIP coefficients are largest.
The final sub-panel of Figure~\ref{fig:astrometricresidual} is a
sanity check on the location of the projected positions, and also
gives some context for our chosen aperture radii of 1, 1.5, and 2.25
pixels.

Finally, we use \texttt{fiphot} to perform aperture photometry on the
bright stars from the
source list, by summing the counts inside appropriately-weighted
circular apertures centered on the projected positions from Gaia DR2. 
The pixel weights $w_{x,y}$ are equal to the fraction of the pixel
that falls within the aperture.  They are thus unity for pixels
entirely within the aperture, and fractional along the aperture
boundary (see \citealt{Pal_2009} Fig 17). 
The background levels are measured in annuli around each aperture
center.  The raw flux of the object after background removal is then
(\citealt{Pal_2009} Eq 65)
\begin{equation}
  f = \sum_{x,y} w_{x,y} (I_{x,y} - B) = f_{\rm total} - B r_0^2.
  \label{eq:simple_aperture_phot}
\end{equation}
The resulting measurements, for instance of the background level of
each aperture, and the number of ``good'' objects that are detected,
are later used to select photometric reference frames.

@@

The core operation of ``classical'' image subtraction
attempts to match a photometric reference $R$ and a target image $I$ by 
computing and applying a convolution kernel.
For ground-based data, this ``match'' typically corrects for
differences in seeing or transparency between the reference and
target; for space-based data, the match might correct for spacecraft
jitter, or thermal and corresponding PSF variations.
The kernel, once applied to the high signal-to noise reference,
produces a model image, $M_{xy}$,
\begin{equation}
    M_{xy} = (R \otimes K)_{xy} + B_{xy},
\end{equation}
where $B_{xy}$ is a component of the model image that allows for
background variations.
We model the background separately, so we set $B_{xy}=0$.
The convolution kernel $K$ is typically decomposed onto a
basis, $K = \sum_i c_i K_i$, and the coefficients are found
by minimizing
\begin{equation}
    \chi^2 = \sum_{xy} \left( \frac{I_{xy} - M_{xy}}{\sigma_{xy}} \right)^2,
    \label{eq:chisq_conv}
\end{equation}
where $\sigma_{xy}$ is the uncertainty in the target image pixel values.
Photometry is then performed on the difference image $D_{xy}$, where
$D_{xy} = I_{xy} - M_{xy}$.
For this work, the uncertainty in each target image pixel is
taken to be a constant.
